Individual Variation in Animal Movement

### 2021-02-14 movement_paper/rudolph_ch2.Rmd
add nathan citation

>>>>

Providing a general framework for movement ecology that allows to link movement patterns and processes, starting with a focus on movement itself and the individual's internal state,navigation capacity, motion capacity, and responses to external factors [@nathan2008movement]. Although it increases the complexity and requires more fine scale data, the framework recognizes how variation at the level of individuals can have consequences at larger ecological scales.

# References
